Ceph Parallel File System Evaluation Report

### 2013-11-06 introduction.tex
fixing based on various review comments

This paper presents our findings on block I/O and file system performance of
Ceph for scientific high-performance computing (HPC) environments. Through
systematic experiments and tuning efforts, we observed that Ceph can perform
close to 80\% of raw hardware bandwidth at object level and close to 70\% of
at file system level. We also identified that Ceph's metadata 
plus data journaling design is a weak spot for a typical

This rest of the paper is organized as follows. Section~\ref{sec:testbed} gives an
overview on our general test and evaluation methodology as well as testbed
environment; Following it, Section~\ref{sec:baseline} establishes the baseline
performance and expectations for all critical components on the data path;
Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
bottom up: from middle tier RADOS object layer to the file system-level and
then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
investigative and tuning effort, we compare results before and after, and how
the process eventually bring the system performance to a respectable state.
Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
and future works.

>>>>

This paper presents our findings on block I/O and file system performance of
Ceph for scientific high-performance computing (HPC) environments. Through
systematic experiments and tuning efforts, we observed that Ceph can perform
close to 80\% of raw hardware bandwidth at object level and close to 70\% of
at file system level. We also identified that Ceph's metadata plus data
journaling design is a weak spot as far as our particular storage
infrastructure is concerned.

This rest of the paper is organized as follows. Section~\ref{sec:background}
provides an overview to Ceph and its architectural components;
Section~\ref{sec:testbed} gives an overview on our general test and evaluation
methodology as well as testbed environment; Following it,
Section~\ref{sec:baseline} establishes the baseline performance and
expectations for all critical components on the data path;
Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
bottom up: from middle tier RADOS object layer to the file system-level and
then meta data performance. In Section~\ref{sec:ceph-tuning} we highlight the
investigative and tuning effort, we compare results before and after, and how
the process eventually bring the system performance to a respectable state.
Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
and future works.

### 2013-11-06 testbed.tex
cutting
fixing based on various review comments

We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. Exported RAID groups (LUNs) by these
controllers are driven by four server hosts (oss-[1-4]).  Each server host has
two InfiniBand (IB) QDR connections to the storage backend.  We used a single
dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
setup is adequate to drive the SFA10K at its maximum theoretical throughput
(roughly 12 GB/s). Server hosts and SFA10K connection diagram is illustrated in
Figure~\ref{fig:ddn-sfa10k}.

\begin{figure}[htb]
\centering
\includegraphics[width=3in]{figs/sfa10k}
\caption{DDN SFA10K hardware and host connection diagram}
\label{fig:ddn-sfa10k}
\end{figure}

@@

Our tools for benchmarking and evaluating different layers also change as we
go up in the stack.  For example, a tool perfect for assessing block-level
performance over a single server host might be completely inadequate for
observing parallel file system performance over multiple clients. As we
present our evaluations, we will also introduce and explain our benchmark
tools along the way.

>>>>

We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. Exported RAID groups (LUNs) by these
controllers are driven by four server hosts (oss-[1-4]).  Each server host has
two InfiniBand (IB) QDR connections to the storage backend.  We used a single
dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
setup is adequate to drive the SFA10K at its maximum theoretical throughput
(roughly 12 GB/s). 
%Server hosts and SFA10K connection diagram is illustrated in
%Figure~\ref{fig:ddn-sfa10k}.

\begin{comment}
\begin{figure}[htb]
\centering
\includegraphics[width=3in]{figs/sfa10k}
\caption{DDN SFA10K hardware and host connection diagram}
\label{fig:ddn-sfa10k}
\end{figure}
\end{comment}

@@

%Our tools for benchmarking and evaluating different layers also change as we
%go up in the stack.  For example, a tool perfect for assessing block-level
%performance over a single server host might be completely inadequate for
%observing parallel file system performance over multiple clients. As we
%present our evaluations, we will also introduce and explain our benchmark
%tools along the way.
